Fusing Filters with Integer Linear Programming

### 2014-05-13 2014betterfusionforfilters/section/04-ILP.tex
Merge cleanup

\begin{figure}[H]
\begin{code}
 normalizeInc :: Array Int -> Array Int
 normalizeInc xs
  = let incs = map  (+1)    us      (A1) (B2)
        sum  = fold (+) 0   us      (A1) (B1)
        norm = map  (/ sum) incs    (A2) (B2)
    in  norm
\end{code}
\end{figure}

For @normalizeInc@, the first approach is to fuse the computation of @incs@ and @sum@ into a single loop (indicated by @A1@), then use a second loop to compute @norm@ (indicated by @A2@). The other approach is to compute @sum@ first (@B1@), and fuse the computation of @incs@ and @norm@ into the second loop (@B2@). For this specific function the second approach seems preferable because it avoids creating the intermediate array @incs@, but for large programs with many operators the optimal way to cluster operators into loops can be entirely non-obvious.

>>>>

\begin{figure}[H]
\begin{code}
 normalizeInc :: Array Int -> Array Int
 normalizeInc xs
  = let incs = map  (+1)    us      (A2) (B1)
        sum  = fold (+) 0   us      (A1) (B1)
        norm = map  (/ sum) incs    (A2) (B2)
    in  norm
\end{code}
\end{figure}
For @normalizeInc@, the first option is to compute @sum@ first (@A1@), and fuse the computation of @incs@ and @norm@ into the second loop (@A2@), as shown in the first graph in Figure~\ref{f:normInc}. The other option is to fuse the computation of @incs@ and @sum@ into a single loop (indicated by @B1@), then use a second loop to compute @norm@ (indicated by @B2@). For this specific function, it is fairly obvious that Option 1 is preferable because it avoids creating the intermediate array @incs@. For large programs with many operators the optimal way to cluster operators into loops can be entirely non-obvious.
